Medical Concept Extraction

### 2012-12-17 paper/paper.tex
Updating Design section header.
Updating results table in paper.
Providing headers for sections.

\section{Background}
\subsection{Related Work}
Concept extraction in medicine is an increasingly well-studied problem. One of the main driving forces behind such research is the annual i2b2/VA Workshop on Natural Language Processing Challenges for Clinical Records, which challenges participants to develop a system for "the extraction of medical concepts from patient reports." Torii et al. \cite{torii}, for example, developed a system using the same training data as us for the workshop. Their concept extraction system was trained using a tagger specifically developed for the biology domain, and their work shows the difficulty in porting trained systems across clinical documents from various sources.

@@

\section{Design}

@@

\section{System}

@@

\section{Results}

@@

\begin{figure}

\begin{center}
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l||l|l|}
	\hline
	\multicolumn{11}{|c||}{\bf Feature Set} & \multicolumn{2}{|c|}{\bf F1 Score}	\\ \hline
	% BEGIN COLUMN HEADERS
		\begin{sideways} length \end{sideways} & 
		\begin{sideways} mitre \end{sideways} & 
		\begin{sideways} next \end{sideways} & 
		\begin{sideways} pos \end{sideways} & 
		\begin{sideways} prev \end{sideways} & 
		\begin{sideways} stem\_lancaster \end{sideways} & 
		\begin{sideways} stem\_porter \end{sideways} & 
		\begin{sideways} stem\_wordnet \end{sideways} & 
		\begin{sideways} test\_result \end{sideways} & 
		\begin{sideways} word \end{sideways} & 
		\begin{sideways} word\_shape \end{sideways} & 
		LIN & CRF	\\ \hline
	% END COLUMN HEAERS

	\checkmark & & & & & & & & & & & &	\\ \hline
	& \checkmark & & & & & & & & & & &	\\ \hline
	& & \checkmark & & & & & & & & & &	\\ \hline
	& & & \checkmark & & & & & & & & &	\\ \hline
	& & & & \checkmark & & & & & & & &	\\ \hline
	& & & & & \checkmark & & & & & & &	\\ \hline
	& & & & & & \checkmark & & & & & &	\\ \hline
	& & & & & & & \checkmark & & & & &	\\ \hline
	& & & & & & & & \checkmark & & & &	\\ \hline
	& & & & & & & & & \checkmark & & &	\\ \hline
	& & & & & & & & & & \checkmark & &	\\ \hline

\end{tabular}
\end{center}
\caption{A summary of the F1-scores from many different models with different features enabled.}
\label{fig:summary_f1_scores}
\end{figure}

>>>>

\section{Background}
This section discusses a limited selection of previous work in concept extraction as well as work done in machine learning that is leveraged in this project.

\subsection{Related Work}
Concept extraction in medicine is an increasingly well-studied problem. One of the main driving forces behind such research is the annual i2b2/VA Workshop on Natural Language Processing Challenges for Clinical Records, which challenges participants to develop a system for "the extraction of medical concepts from patient reports." Torii et al. \cite{torii}, for example, developed a system using the same training data as us for the workshop. Their concept extraction system was trained using a tagger specifically developed for the biology domain, and their work shows the difficulty in porting trained systems across clinical documents from various sources.

@@

\section{Design}
This section describes the design of our system. Specifically, it details the classification task and the linguistic features our system utilizes in order to perform classification.

@@

\section{System}
This section discusses the framework code we have developed in order to perform concept extraction, the web service frontend which allows users to test the service without seeing any of the underlying data, and the machine learning libraries that are leveraged.

@@

\section{Results}
This section discusses the data set, the models that were trained as part of the project, the (excessive) amount of time taken to train them, and the performance of those models on the test data.

@@

\begin{figure*}
\begin{center}
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l||l|l|}
	\hline
	\multicolumn{11}{|c||}{\bf Feature Set} & \multicolumn{2}{|c|}{\bf F1 Score}	\\ \hline
	% BEGIN COLUMN HEADERS
		\begin{sideways} length \end{sideways} & 
		\begin{sideways} mitre \end{sideways} & 
		\begin{sideways} next \end{sideways} & 
		\begin{sideways} pos \end{sideways} & 
		\begin{sideways} prev \end{sideways} & 
		\begin{sideways} stem\_lancaster \end{sideways} & 
		\begin{sideways} stem\_porter \end{sideways} & 
		\begin{sideways} stem\_wordnet \end{sideways} & 
		\begin{sideways} test\_result \end{sideways} & 
		\begin{sideways} word \end{sideways} & 
		\begin{sideways} word\_shape \end{sideways} & 
		LIN & CRF	\\ \hline
	% END COLUMN HEAERS

	\checkmark & & & & & & & & & & & 0.2157 & 0.0420	\\ \hline
	& \checkmark & & & & & & & & & & 0.2155 & 0.0927	\\ \hline
	& & \checkmark & & & & & & & & & 0.2155 & 0.0572	\\ \hline
	& & & \checkmark & & & & & & & & 0.2155 & 0.0820	\\ \hline
	& & & & \checkmark & & & & & & & 0.2155 & 0.0366	\\ \hline
	& & & & & \checkmark & & & & & & 0.7085 & 0.2878	\\ \hline
	& & & & & & \checkmark & & & & & 0.7266 & 0.2886	\\ \hline
	& & & & & & & \checkmark & & & & 0.7309 & 0.2857	\\ \hline
	& & & & & & & & \checkmark & & & 0.2806 & 0.1084	\\ \hline
	& & & & & & & & & \checkmark & & 0.7332 & 0.2753	\\ \hline
	& & & & & & & & & & \checkmark & 0.2431 & 0.1244	\\ \hline

\end{tabular}
\end{center}
\caption{A summary of the F1-scores from many different models with different features enabled.}
\label{fig:summary_f1_scores}
\end{figure*}
